\section{User characteristics}

The main actors who interact with the application will be presented under this section. 

\begin{itemize}
    \item \emph{Visitors}: They are not registered users, the system allows them to register through a sign up service either to Data4Help, becoming individuals or third-parties, or to Track4Run, becoming organizers. The application lets them also to be spectators of a run organized with Track4Run service. 
    \item \emph{Individuals}: They are single users registered to Data4Help service. It means that the system lets them to sign in, in order to interact with the application either to accept or refuse the third-party single user requests or monitor their acquired data.
    \item \emph{Third-parties}: They are companies that are registered to Data4Help. Also in this case, the application provides a sign in service, so as to let companies to interact and perform single and groups requests. 
    \item \emph{Ambulance service}: The software has to interact with the ambulance service  to provide a non-‐intrusive SOS service to elderly people, in case of illness. The application sends the exact position where the ambulance has to go.  
    \item \emph{Elderly people}: They are Individuals, the software allows them to subscribe to an SOS service provided by AutomatedSOS, through their Data4Help account (they must have one). 
    \item \emph{Map service}: The application needs to interact with the map service, such as \emph{Google Maps}, in order to let visitors and users to see on a map the position of all runners during the run.
    \item \emph{Organizers}: They are companies that are registered to Track4Run service. The system provides them a sign in interface and, after login, lets them organize runs. They don't need to be registered to Data4Help.
    \item \emph{Runners}: They are individuals, the application makes them able to enroll in a race through their Data4Help account (they must have one).
\end{itemize}