\section{Design Constraints}
    \subsection{Standards compliance}
        
        Since the software is initially meant to be used in Italy, it is important for it to be compliant towards the \emph{General Data Protection Regulation} (GDPR) recently approved in Europe. This means that the software always has to:
        \begin{itemize}
            \item ask for the user approval when retrieving and using his/her data;
            \item allow him/her to know what data is being shared and with whom;
            \item make it possible for him/her to revoke the consent at any time.
        \end{itemize}
        
    \subsection{Hardware limitations}
    
        In order to function properly, the three services need that some categories of users associate their smart-watch or fitness band to them. This concerns:
        \begin{itemize}
            \item Individuals for D4H;
            \item Elderly people for ASOS;
            \item Participants for T4R.
        \end{itemize}
        Note that both Elderly people and Participants must have a D4H account as Individuals in order to benefit from ASOS and T4R, respectively.
        
        Moreover, the devices of all the user need to have an active internet connection in order for the software to work.
        
    \subsection{Operative Systems}  \label{OS}
        
        The services will have to run on both Android and iOS. The Android version needs to work under Android 4.4 and above, while the iOS one has to support iOS 10 and above, so as to cover the majority of devices.