\chapter{Introduction}

\section{Purpose}
    This document will provide an analysis of requirements and specifications of three new services the \emph{TrackMe} company is willing to launch.\\
    \emph{TrackMe} is a company that wants to develop a software-based service allowing Third-parties to monitor the location and health status of individuals.
    Said services are described below.

\subsection{Data4Help}
    \textbf{\emph{Data4Help}} allows \emph{TrackMe} to gather data from Users and to provide them to Third-parties upon request. In particular, it has the following goals:
    \begin{itemize}
        \item $[G1.1]$ Third-parties have to be able to monitor the location and health status of individuals.
        \item $[G1.2]$ Third-parties have to be able to request data of a single user through his/her fiscal code.
        \item $[G1.3]$ Third-parties have to be able to request data of groups of Users.
        \item $[G1.4]$ Third-parties have to be able to subscribe to user data, specifying the frequency of updates and the desired granularity of data.
        \item $[G1.5]$ Users have to be able to decide whether share their not anonymised data (gathered through smart devices) or not.
    \end{itemize}

\subsection{AutomatedSOS}    
    \textbf{\emph{AutomatedSOS}} lets Third-parties provide assistance to elderly people in case of sudden illness by sending them an ambulance. Hence, its goals are:
    \begin{itemize}
        \item $[G2.1]$ Elderly people's health status have to be constantly monitored.
        \item $[G2.2]$ An ambulance has to arrive to Elderly people's location when their vital signs go below a certain threshold.
        %specify threshold?
    \end{itemize}
    
\subsection{Track4Run}
    \textbf{\emph{Track4Run}} allows the organisation of runs, the subscription to them and the tracking of runners through \emph{Data4Help} gathered location. These are the objective the service aims to achieve:
    \begin{itemize}
        \item $[G3.1]$ Organisers have to be able to define the details of runs.
        \item $[G3.2]$ Participants have to be able to enrol to runs.
        \item $[G3.3]$ Spectators have to be able to track Participants' position on a map.
    \end{itemize}

\section{Scope}
    