\section{Purpose}
    This document will provide an analysis of requirements and specifications of three new services the \emph{TrackMe} company is willing to launch.\\
    \emph{TrackMe} is a company that wants to develop a software-based service allowing Third-parties to monitor the location and health status of individuals.
    Said services are described below.

\subsection{Data4Help}
    \textbf{\emph{Data4Help}} allows \emph{TrackMe} to gather data from Users and to provide them to Third-parties upon request. In particular, it has the following goals:
    \begin{enumerate}[label={[}G1.\arabic*{]}]
        \item Third-parties have to be able to monitor the location and health status of Individuals.
        \item Third-parties have to be able to request data of an Individual through his/her fiscal code.
        \item Third-parties have to be able to request data of groups of Individuals.
        \item Third-parties have to be able to subscribe to user data, specifying the frequency of updates and the desired granularity of data.
        \item Individuals have to be able to decide whether share their not anonymised data (gathered through smart devices) or not and to see what they are sharing to whom.
    \end{enumerate}

\subsection{AutomatedSOS}    
    \textbf{\emph{AutomatedSOS}} lets Third-parties provide assistance to Elderly people in case of sudden illness by sending them an ambulance. Hence, its goals are:
    \begin{enumerate}[label={[}G2.\arabic*{]}]
        \item Elderly people's health status has to be constantly monitored.
        \item An ambulance has to arrive to Elderly people's location when their vital signs go below a certain threshold.
        %specify threshold?
    \end{enumerate}
    
\subsection{Track4Run}
    \textbf{\emph{Track4Run}} allows the organisation of runs, the subscription to them and the tracking of runners through \emph{Data4Help} gathered location. These are the objective the service aims to achieve:
    \begin{enumerate}[label={[}G3.\arabic*{]}]
        \item Organisers have to be able to define the details of runs.
        \item Runners have to be able to enrol to runs.
        \item Visitors have to be able to track Participants' position on a map.
    \end{enumerate}